---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dcsbm

<!-- badges: start -->
<!-- badges: end -->

The goal of dcsbm is to provide methods for estimating a two-way degree corrected stochastic block model for directed, weighted graphs. 
Uses the 'igraph' library <https://igraph.org> for graph handling. 
See Peixoto (2014) <10.1103/PhysRevE.89.012804> for details on the inference algorithm.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mpff/dcsbm")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dcsbm)
library(igraph)

# Generate graph by a planted partition model.
partition <- sample(1:3, 30, replace = T)
g <- sample_ppm(partition, 0.25, 0.01)
V(g)$color <- partition
plot(g)
```
