---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "66%"
)
set.seed(2022)
```

# dcsbm

<!-- badges: start -->
[![R-CMD-check](https://github.com/mpff/dcsbm/workflows/R-CMD-check/badge.svg)](https://github.com/mpff/dcsbm/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/mpff/dcsbm/branch/main/graph/badge.svg)](https://app.codecov.io/gh/mpff/dcsbm?branch=main)
<!-- badges: end -->

The goal of dcsbm is to provide methods for estimating a two-way degree corrected stochastic block model for directed, weighted graphs. 
Uses the 'igraph' library <https://igraph.org> for graph handling. 
See Peixoto (2014) <10.1103/PhysRevE.89.012804> for details on the inference algorithm.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mpff/dcsbm")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dcsbm)

# Generate graph by a planted partition model and estimate a degree-corrected SBM.
g <- sample_dcppm(60, c=0.9, k=10, B=3, k_coef=1.5, directed=TRUE, loops=TRUE)
m <- dcsbm(g, degree_correction=TRUE, n.sweeps=5, verbose=FALSE)

# Show model summary.
summary(m)

# Plot the resulting partition.
plot(g, vertex.color = m$best_partition, vertex.label = NA, sub = "Estimated partition")

```
