---
title: "Introduction to the dcsbm package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the dcsbm package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
set.seed(2022)
```


You can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mpff/dcsbm")
library(dcsbm)
```


#### 1. No degree correction

We can simulate a network with a clear block structure using the planted partition model via `sample_ppm`. And then estimate a SBM using the `dcsbm` function.

```{r}
G <- sample_ppm(60, 0.9, 5, 3, directed = TRUE, loops = TRUE)

model <- dcsbm(G, n.sweeps = 1, verbose = FALSE)
 
plot(G, vertex.color = model$best_partition, vertex.label = NA, sub = "Estimated partition")
```


#### 2. With degree correction

We can simulate a planted partition network with additional degree variability inside each block via `sample_dcppm`. And then estimate a degree corrected SBM by using `dcsbm` and setting `degree_correction = TRUE`.

```{r}
G <- sample_dcppm(60, 0.9, 5, 3, k_coef = 2, directed = TRUE, loops = TRUE)

model <- dcsbm(G, degree_correction = TRUE, n.sweeps = 5, verbose = FALSE)
 
plot(G, vertex.color = model$best_partition, vertex.label = NA, sub = "Estimated partition")
plot(G, vertex.color = c(rep(1,20), rep(2,20), rep(3,20)), vertex.label = NA, sub = "True partition")
```
